Pillar 2- Quick Topic Models

### 2019-04-30 Pillar 2 - Tmp Topic Modeling.Rmd
65 topics

#Plot
plot_evaluation("catalogues")
#plot_evaluation("manuals")
```
##Best model
We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
```{r best model, eval = F}
load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted

catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "35") %>% pull(Model) %>%.[[1]]

>>>>

#Plot
plot_evaluation("catalogues")
#plot_evaluation("manuals")
```
##Best model
We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with mode burns and iterations
```{r best model, eval = T}
load("./Output/catalogues_tmp_topic_model_tibble.RDATA") #do not run this if knitted

catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]
